\Huge Conferences in an Era of Expensive Carbon

### 2019-12-26 main.tex
Final changes for CACM version

Indeed, scientific societies have an especially important role to
play, since, for many members, travel to conferences represents a
substantial or even dominant part of their individual contribution to
climate change.  A single round-trip flight from Philadelphia to Paris emits
the equivalent of about 1.8 tons of carbon dioxide (\COtwoE, or informally
``carbon'') per
passenger~\cite{carboncalculator}. This is a significant fraction of the
{\em total} yearly emissions for an average resident of the US (16.5 tons)
or Europe (7 tons)~\cite{emissions}.
Moreover, these emissions have no near-term technological
fix, as jet fuel is difficult to replace with renewable energy
sources~\cite{elec-air}.

@@

Ultimately, however, carbon offsets and other ``good works'' cannot
substitute for real reductions in emissions~\cite{anderson2012inconvenient,
  carbon-offsets-are-not-our-get-out-jail-free-card}: they are, at best, a
short-term expedient that buys time to agree on more
difficult cuts.
%
Indeed, the main goal of carbon pricing should be to stimulate creative
rethinking of the conference model itself---for example, seriously
considering alternatives such as rapid-turnaround journal-only publishing
models, yearly megaconferences, and entirely virtual
conferences~\cite{NCN}.
%
A potential sticking point is that some of these will significantly reduce
conference revenues, in turn impacting the income stream of ACM itself; this
could make emissions reduction politically problematic unless ACM's
conference-focused business model is also adjusted.

>>>>

Indeed, scientific societies have an especially important role to
play, since, for many members, travel to conferences represents a
substantial or even dominant part of their individual contribution to
climate change.  A single round-trip flight from Philadelphia to Paris emits
the equivalent of about 1.8 tons of carbon dioxide (\COtwoE, or informally
``carbon'') per
passenger~\cite{ClimateCommittee}. This is a significant fraction of the
{\em total} yearly emissions for an average resident of the US (16.5 tons)
or Europe (7 tons)~\cite{emissions}.
Moreover, these emissions have no near-term technological
fix, as jet fuel is difficult to replace with renewable energy
sources~\cite{elec-air}.

@@

Ultimately, however, carbon offsets and other ``good works'' cannot
substitute for real reductions in emissions~\cite{anderson2012inconvenient,
  carbon-offsets-are-not-our-get-out-jail-free-card}: they are, at best, a
short-term expedient that buys time to agree on more
difficult cuts.
%
Indeed, the main goal of carbon pricing should be to stimulate creative
rethinking of the conference model itself---for example, seriously
considering alternatives such as rapid-turnaround journal-only publishing
models, yearly mega-conferences, and entirely virtual
conferences~\cite{NCN}.
%
A potential sticking point is that some of these will significantly reduce
conference revenues, in turn impacting the income stream of ACM itself; this
could make emissions reduction politically problematic unless ACM's
conference-focused business model is also adjusted.
